---
title: "Presentazione"
author: "Enrico Cominato"
date: "11 febbraio 2019"
output: 
  html_notebook
runtime: shiny
---

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
  .shiny-input-checkboxgroup.shiny-input-container-inline label ~ .shiny-options-group, .shiny-input-radiogroup.shiny-input-container-inline label ~ .shiny-options-group {
    margin-top: -1px;
    margin-left: auto;
    margin-right: auto;
    width: 800px !important;
  }
  .irs{
    width: 800px !important;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(corrplot)
# per caricare
#library(rsconnect)
#rsconnect::deployApp('applicazione.Rmd')

# dataset delle partite fatte
dataset_games <- read_csv("dataset/games.csv")

# preferisco:
# 1: spaccare data e ora
# 2: mettere il risultato della partita come un booleano
games <- dataset_games %>%
  mutate(period = as.Date(added,format = "%Y-%m", tz = "UTc") ) %>%
  mutate(result = if_else(result=="win", TRUE, FALSE)) %>%
  select(everything() , -added)

# dataset delle giocate fatte in ogni partita
#dataset_plays <- read_csv("dataset/plays.csv")

# periodo di validità del dataset
start <- (games %>%
  select(period) %>%
  group_by(period) %>%
  arrange(period) %>%
  head(1) )[[1]]

end <- (games %>%
  select(period) %>%
  group_by(period) %>%
  arrange(desc(period)) %>%
  head(1))[[1]]

filter_by_date <- function(ds,range ){
return( ds %>%
          filter(
            between(as.Date(period,"%Y-%M"),
                    as.Date(range[1],"%Y-%M"),
                    as.Date(range[2],"%Y-%M")
                    ) 
          )
      )
}
filter_by_class <- function(ds,selector){
  # se non ho selezionato una classe le ritorno tutte
  if (is.null(selector) ){ return(ds) }
  # seleziono solo le classi scelte
  return( ds %>%
    filter( class %in% selector )
  )
}

# per stampe e filtri vari
classi <- c("Druid", 
            "Hunter", 
            "Mage",
            "Paladin",
            "Priest",
            "Rogue",
            "Shaman",
            "Warlock",
            "Warrior")

colori <- c("Druid"="brown", 
            "Hunter"="green", 
            "Mage"="aquamarine",
            "Paladin"="yellow",
            "Priest"="grey",
            "Rogue"="black",
            "Shaman"="blue",
            "Warlock"="blueviolet",
            "Warrior"="red")

icone <- c(
  "https://hsreplay.net/static/images/class-icons/druid.png",
  "https://hsreplay.net/static/images/class-icons/hunter.png",
  "https://hsreplay.net/static/images/class-icons/mage.png",
  "https://hsreplay.net/static/images/class-icons/paladin.png",
  "https://hsreplay.net/static/images/class-icons/priest.png",
  "https://hsreplay.net/static/images/class-icons/rogue.png",
  "https://hsreplay.net/static/images/class-icons/shaman.png",
  "https://hsreplay.net/static/images/class-icons/warlock.png",
  "https://hsreplay.net/static/images/class-icons/warrior.png"
)
```
## Introduction

In this presentation we will analize the card game Hearthsone.
- We will see how the "meta" has changed through the years, which decks have been played and we will try to figure out why they haev been played.
- After that, there will be an analysis of each single card used in the game not only the frequency of usage during time but also we will try to figure out how a single card can have an impact on the game.
- At the end there will be "mithbuster time" were we try to find if tips and advise from pro player are really useful or just mith.

All the data are available [here](http://www.hearthscry.com/). Here we have loaded data from `r start` to `r end`.

## First analysis
Let's prepare the data. **TESTO DA FARE**

```{r class winrate computation, echo=TRUE}
# class winrate
class_hero <- games %>%
  group_by(hero, period) %>%
  summarize(wins = sum(result), games = n()) %>%
  rename(class = hero) %>%
  ungroup()

class_oppo <- games %>%
  group_by(opponent, period) %>%
  summarize(wins = sum(result), games = n()) %>%
  rename(class = opponent) %>%
  ungroup()

class_total <- class_hero %>%
  left_join(class_oppo, by = c("class", "period")) %>%
  group_by(class, period) %>%
  summarize(wins = wins.x+wins.y, games = games.x+games.y, winrate = wins/games)
```

Here we have an example of the resulting data of the last day. **TESTO DA FARE**
```{r class winrate table view, echo=FALSE}
class_total$class <- as.factor(class_total$class)
# vediamo i dati
knitr::kable(
  class_total %>% filter(period == end), 
  caption = "Class winrate over time"
)

```

## Guardiamo un po' il winrate di ogni classe {#title .emphasized }

We can select one or more classes (if none there will be displayed all)
    
```{r}
inputPanel(
  checkboxGroupInput("class_selector", "Classi",
    choiceNames = mapply(classi, icone, FUN = function(classe, iconeUrl) {
      tagList(
        tags$img(src=iconeUrl, width=50, height=50),
        ""
      )
    }, SIMPLIFY = FALSE, USE.NAMES = FALSE),
    choiceValues = classi,
    inline = TRUE
  ),
  textOutput("txt")
)
```
And we can select a specific period of time.

```{r}
inputPanel(
#Add a Slider Input to select date range
  sliderInput(inputId = "Date_range_selector",
             label ="Select Date Range",
             min = start,
             max = end,
             value = c(start,end),
             step = 30,
             timeFormat="%Y-%m")
)
```   
 
So, this is our winrate for each class...but this is not tellig us a lot.
In the next step we'll try to find out why a specific class has that winrate in that period.
    
```{r}
filter_by_date <- function(ds,range ){
return( ds %>%
          filter(
            between(as.Date(period,"%Y-%M"),
                    as.Date(range[1],"%Y-%M"),
                    as.Date(range[2],"%Y-%M")
                    ) 
          )
      )
}
filter_by_class <- function(ds,selector){
  # se non ho selezionato una classe le ritorno tutte
  if (is.null(selector) ){ return(ds) }
  # seleziono solo le classi scelte
  return( ds %>%
    filter( class %in% selector )
  )
}

renderPlot({
  class_total %>%
    filter_by_date(input$Date_range_selector)%>%
      filter_by_class(input$class_selector)%>%
        ggplot(aes(x = period, y = winrate)) + 
          geom_smooth(aes(color = factor(class)), se = FALSE) +
            scale_color_manual( values = colori)
})
```
## Presence on the game {#title .emphasized }
First of all we want to know if the number of player that use a specific class can influence the meta. So we plot the number of games per class.

```{r presence computation}
class_total <- class_total %>%
  group_by(period) %>%
  mutate(total_games_per_day = sum(games)) %>%
  ungroup() %>%
  mutate(presence = games/total_games_per_day)

# vediamo i dati
knitr::kable(
  class_total %>% filter(period == end), 
  caption = "Class winrate over time"
)
```

You can use the filters above to see speific class or period.

```{r presence plot}
renderPlot({
  class_total %>%
    filter_by_date(input$Date_range_selector)%>%
      filter_by_class(input$class_selector)%>%
        ggplot(aes(x = period, y = presence)) + 
          geom_smooth(aes(color = factor(class)), se = FALSE) +
            scale_color_manual( values = colori)
})
```
What is the correlation between the number of player that are using a specific class and his winrate?

```{r}
inputPanel(
#Add a Slider Input to select date range
  sliderInput(inputId = "Date_range_selector_correlation",
             label ="Select Date Range",
             min = start,
             max = end,
             value = c(start,end),
             step = 30,
             timeFormat="%Y-%m")
)
``` 

```{r correlation presence winrate plot}
renderPlot({
  M <- cor(class_total %>% 
             filter(class == "Shaman") %>%
             filter_by_date(input$Date_range_selector_correlation) %>%
              select(winrate, presence)
          )
  corrplot(M, method = "ellipse")
})
```

This seems not really helpful 

Let's analyze the correlation between the winrate of different classes and see if we can understand somenthing more from the information about the presence of those classes in the game

```{r winrate correlation computation}
winrate_correlation <- tibble(
  "Druid winrate" = class_total %>%
  filter(class == "Druid", period == end) %>%
  select(period,winrate)
)

add_column(
  winrate_correlation,
  "Priest winrate" = class_total %>%
  filter(class == "Priest", period == end) %>%
  select(period,winrate)
)

# winrate_correlation <- class_total %>%
#   group_by(class, period) %>%
#   select(class,period,winrate) %>%
#   ungroup()

# vediamo i dati
knitr::kable(
  winrate_correlation %>% filter(period == end), 
  caption = "Class winrate over time"
)
```